### 2022-12-19 abstract.tex
last polish of intro?
paper 1 polish

Possible answers to this question are given in the first and largest part of
this thesis. It consists of three extensions to a recently proposed
reverse-Bayes method for quantifying replication success. The key idea of the
method is to challenge the data from the original study with a sceptical prior
distribution so that the resulting posterior distribution no longer indicates
evidence for an effect. The goal of the replication study is then to show that
the sceptical prior is unrealistic, and replication success is achieved if there
is sufficient conflict between the prior and the replication data. The procedure
can be summarized in a single quantitative measure, termed the sceptical
$p$-value.
% extension 1
The first extension recalibrates the sceptical $p$-value so that replication
success takes effect size more appropriately into account. Specifically, the
recalibration is chosen such that for original studies which were borderline
significant, replication success can only be achieved if the effect estimate
from the replication study is larger than the effect estimate from the original
study. We find that the recalibrated sceptical $p$-value has good frequentist
properties comparable to the standard method used in practice.
% extension 2
The second extension replaces tail probabilities with Bayes factors as measures
of evidence. The procedure can again be summarized in a single measure called
the sceptical Bayes factor.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
% We find that the extended method combines two notions of replicability: It
% requires that original and replication study independently provide evidence for
% an effect and ensures that their effect estimates are compatible.
The sceptical Bayes factor has similar properties as the sceptical $p$-value but
it avoids a statistical paradox which the sceptical $p$-value suffers from -- in
some situations the sceptical $p$-value may indicate replication success even
though the effect estimate from the replication is much smaller than the effect
estimate from the original study. % , which cannot happen with the sceptical
% Bayes factor.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. This approach can lead to potentially more efficient designs compared
to classical approaches, and it can be used for replication design based on both
the sceptical $p$-value and the sceptical Bayes factor.
% External knowledge, such as data from other studies, is ubiquitous in the
% replication setting and taking it into account can lead to potentially more
% efficient designs compared to classical approaches.

>>>>

Possible answers to this question are given in the first and largest part of
this thesis. It consists of three extensions to a recently proposed
reverse-Bayes method for quantifying replication success. The key idea of the
method is to challenge the data from the original study with a sceptical prior
distribution so that the resulting posterior distribution no longer indicates
evidence for an effect. The goal of the replication study is then to show that
the sceptical prior is unrealistic, and replication success is achieved if there
is sufficient conflict between the prior and the replication data. The procedure
can be summarized in a single quantitative measure, termed the sceptical
$p$-value.
% extension 1
The first extension recalibrates the sceptical $p$-value so that replication
success takes effect size more appropriately into account. Specifically, the
recalibration is chosen such that for original studies which were borderline
significant, replication success can only be achieved if the effect estimate
from the replication study is larger than the effect estimate from the original
study. We find that the recalibrated sceptical $p$-value also has good
frequentist properties comparable to the standard method used in practice.
% extension 2
The second extension replaces tail probabilities with Bayes factors as measures
of evidence. The procedure can again be summarized in a single measure called
the sceptical Bayes factor.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
% We find that the extended method combines two notions of replicability: It
% requires that original and replication study independently provide evidence for
% an effect and ensures that their effect estimates are compatible.
The sceptical Bayes factor has similar properties as the sceptical $p$-value but
it avoids a statistical paradox which the sceptical $p$-value suffers from -- in
some situations the sceptical $p$-value may indicate replication success even
though the effect estimate from the replication is arbitrarily smaller than the
effect estimate from the original study. % , which cannot happen with the sceptical
% Bayes factor.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. This approach can lead to potentially more efficient designs compared
to classical approaches, and it can be used for replication design based on both
the sceptical $p$-value and the sceptical Bayes factor.
% External knowledge, such as data from other studies, is ubiquitous in the
% replication setting and taking it into account can lead to potentially more
% efficient designs compared to classical approaches.

### 2022-12-19 intro.Rnw
paper 1 polish

The perceived value of replication studies has changed over the past decade.
Earlier criticisms of low research standards \citep{Altman1994, Ioannidis2005}
were backed up by empirical evidence. For instance, pharmaceutical companies
reported surprisingly low replication rates from pre-clinical research
\citep{Begley2012} followed by later studies estimating that %\$28 billion
billions are wasted each year on flawed and non-replicable research in medicine
and the life sciences \citep{Chalmers2014, Freedman2015, Glasziou2018}.
Similarly, reports of fraud \citep{Wicherts2011} and questionable research
practices \citep{Wagenmakers2011, Simmons2011, John2012} sparked intense
discussion about the need for better research standards in psychology and the
social sciences. These discussions eventually culminated in large-scale
replication projects conducted by huge researcher consortia in fields such as
psychology \citep{Opensc2015, Klein2014, Klein2018, Protzko2020}, economics
\citep{Camerer2016}, the social sciences \citep{Camerer2018}, experimental
philosophy \citep{Cova2018}, and cancer biology \citep{Errington2021}.

>>>>

The perceived value of replication studies has changed over the past decade.
Earlier criticisms of low research standards \citep{Altman1994, Ioannidis2005}
were backed up by empirical evidence. For instance, pharmaceutical companies
reported surprisingly low replication rates from pre-clinical research
\citep{Begley2012} followed by later studies estimating that %\$28 billion
billions are wasted each year on flawed and non-replicable research in medicine
and the life sciences \citep{Chalmers2014, Freedman2015, Glasziou2018}.
Similarly, reports of fraud \citep{Wicherts2011} and questionable research
practices \citep{Wagenmakers2011, Simmons2011, John2012} sparked intense
discussion about the need for better research standards in psychology and the
social sciences. These discussions eventually led to large-scale replication
projects conducted by huge researcher consortia in fields such as psychology
\citep{Opensc2015, Klein2014, Klein2018, Protzko2020}, economics
\citep{Camerer2016}, the social sciences \citep{Camerer2018}, experimental
philosophy \citep{Cova2018}, and cancer biology \citep{Errington2021}.
